---
title: "Gun Control Chi-Square"
author: "Laura Ingulsrud"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This: I'm Laura and I'm updating this markdown file here.

```{r}

library(tidyverse)
gc_df <- read_csv("gc_df.csv")

```

We are asking: Is there a significant difference in recommended gun control action for male and female respondents (should guns be easier, harder, or the same difficulty to get)?

Hey Laura, I made some changes to this document. Sea ya later!

Sup Lauren! Looking gewd

Laura: data wrangling and counts

Chi-square: asks question: are proportions across groups so different that we actually think there's a sig diff between groups?

```{r}

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% # within the gender column, count how many make_get_guns show up
  spread(make_get_guns, n) %>% # different levels in the make_get_guns column are in separate columns by n
  select(-gender)

rownames(get_guns) <- c("Female", "Male") # take the get_guns dataframe and assign row names that are Male and Female

```

My name is Lauren B Jack, the collaborator, and I am going to be a chi-square test for independence!!! 

We ask: "Is there a significant association between sex and opinion on whether guns should be more difficult, easier, or the same difficulty to get?"

```{r}

#Let's look at the acctual proportions:

guns_prop <- prop.table(as.matrix(get_guns), 1) # <- gives a margin over which I would want to calculate a proportion


#Run chi-square test for independence

guns_x2 <- chisq.test(get_guns)

guns_x2

```

"Recommended government action on gun access differed significantly between male (n = ) and female (n= ) respondents ($\chi^2$(`r guns_x2$parameter`) =....., p<0.001). Notably a much higher proportion of female respondents (57.4%) recommend making it more difficult to get guns, compare to 40.4% for male respondents."
